HTW Model

### 2024-02-22 Model/htw_model.qmd
take toc off model results page to make viewing easier

---
title: HTW Model
author: Thomas Gorman
date: "`r Sys.Date()`"
page-layout: full
code-fold: true
code-tools: true
execute: 
  warning: false
  eval: true
---

@@

The posterior distributions of the $c$ and $lr$ parameters are shown @fig-htw-post-dist (i.e. these plots combine all the posterior samples from all of the subjects). There were substantial individual differences in the posteriors of both parameters, with the within-group individual differences generally swamped any between-group or between-model differences. The magnitude of these individual differences remains even if we consider only the single best parameter set for each subject.

>>>>

---
title: HTW Model
author: Thomas Gorman
date: "`r Sys.Date()`"
page-layout: full
code-fold: true
code-tools: true
toc: false
execute: 
  warning: false
  eval: true
  cache: true
---

@@

The posterior distributions of the $c$ and $lr$ parameters are shown @fig-htw-post-dist (i.e. these plots combine all the posterior samples from all of the subjects). There were substantial individual differences in the posteriors of both parameters, with the within-group individual differences generally swamping any between-group or between-model differences. The magnitude of these individual differences remains even if we consider only the single best parameter set for each subject.
